---
title: "p8105_hw1_wy2369"
date: September 22 
output: github_document
---

# Problem 1


### Load the `penguins` dataset 

Here is the code shown below:
```{r}
data("penguins", package = "palmerpenguins")
```

### Write a short description

```{r}
summary(penguins)
```


There are **8** important variables in the dataset which are **species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year**. 

```{r}
nrow(penguins)
```

```{r}
ncol(penguins)
```
The data frame has **`r nrow(penguins)`** rows, and **`r ncol(penguins)`** columns. 

```{r}
Mean = mean(penguins$flipper_length_mm, na.rm = TRUE)
```

The mean of filpper length is equal to **`r Mean`**. 


### Make a scatterplot using `ggplot`

Here is the code to make the scatterplot of flipper_length_mm (y) vs bill_length_mm (x) and color by three species:
```{r message = FALSE, warning = FALSE}
library(ggplot2)

ggplot(penguins,aes(x = bill_length_mm,y = flipper_length_mm,color = species)) + geom_point()

```

The scatterplot looks good and we save it using `ggsave`:
```{r warning = FALSE}
ggsave("scatterplot_hw1.pdf")
```



# Problem 2


### Create a data frame

Load the `tidyverse` and make dataframe: 
```{r message =  FALSE}
library(tidyverse)
p2_df = tibble(
  vec_df = rnorm(10),
  vec_logical = vec_df > 0,
  vec_char = c("A","B","C","D","E","F","G","H","I","J"),
  vec_factor = factor(c("small","small","small","medium","medium","medium","large","large","large","small"))
)
```

### Take the mean value

Use the `pull` function to take the mean of each variable in my dataframe
```{r}
mean(pull(p2_df,vec_df))
mean(pull(p2_df,vec_logical))
mean(pull(p2_df,vec_char))
mean(pull(p2_df,vec_factor))
```

For `vec_df` and `vec_logical`, the mean value can be determined. However, the mean output of `vec_char` and `vec_factor` are NA because they are not numeric or logical variables. 


### Convert the variables

Apply the `as.numeric` function to the logical, character, and factor variables 
```{r eval = FALSE}
as.numeric(pull(p2_df,vec_logical))
as.numeric(pull(p2_df,vec_char))
as.numeric(pull(p2_df,vec_factor))
```


Using the code chunk, logical variable is converted to number (1 or 0), which represents TURE or FALSE. Also factor variable can be converted to number. The default ordering is alphabetical, which means "high" is assigned to be 1, "medium" is 2, and "small" is 3. Because of that, logical and factor variables can take the mean.


However the character variable cannot calculate mean value, because it cannot be converted to numeric variable successfully. Using `as. numeric` code, the mean value of character vector is still NA. 