---
title: "p8105_hw1_wy2369"
date: September 22 
output: github_document
---

# Problem 1

### Load the `penguins` dataset 

Here is the code shown below:
```{r}
data("penguins", package = "palmerpenguins")
```

### A short description of the dataset

First of all, here are **8** important variables in the dataset which are **species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year**. 


##### The size of the dataset:
```{r}
nrow(penguins)
```

```{r}
ncol(penguins)
```
The data frame has `r nrow(penguins)` rows, and `r ncol(penguins)` columns. 


##### Calculate the mean flipper length:
```{r}
Mean = mean(penguins$flipper_length_mm, na.rm = TRUE)
```
The mean is equal to `r Mean`. 

### A scatterplot using `ggplot`
Here is the code to make the scatterplot and color by three species:
```{r message = FALSE}
library(tidyverse)

ggplot(penguins,aes(x = bill_length_mm,y = flipper_length_mm,color = species)) + geom_point()

```

The scatterplot looks good and we save it using `ggsave`:
```{r}
ggsave("scatterplot_hw1.pdf")
```

# Problem 2

### Create a data frame
```{r}

```


